Statistical Theory\\ Chess Dataset Analysis

### 2024-09-30 Article/Article.tex
Updated Article

\subsection{Kolmogorov-Smirnov Test for Normality}
The Kolmogorov-Smirnov (KS) test for normality evaluates whether a sample comes from a normal distribution. It uses the empirical cumulative distribution function (ECDF), $F_n(x)$, of the sample and compares it to the cumulative distribution function (CDF) of the normal distribution, $F(x)$. The test statistic, $D_n$, is defined as:
\[D_n = \sup_x |F_n(x) - F(x)|\]

@@

The KS test is sensitive to both location and shape differences, but less powerful in detecting deviations in the tails of the distribution when compared to other tests like Shapiro-Wilk or Anderson-Darling.

\subsection{Correlation Matrix}
A correlation matrix is a table that displays the pairwise correlation coefficients between multiple variables in a dataset. Each element in the matrix represents the degree of linear relationship between two variables, typically measured by Pearson's correlation coefficient:
\[r_{XY} = \frac{Cov(X,Y)}{\sigma_X\sigma_Y}\]

@@

>>>>

\subsection{Kolmogorov-Smirnov Test}
The Kolmogorov-Smirnov (KS) test for normality evaluates whether a sample comes from a normal distribution. It uses the empirical cumulative distribution function (ECDF), $F_n(x)$, of the sample and compares it to the cumulative distribution function (CDF) of the normal distribution, $F(x)$. The test statistic, $D_n$, is defined as:
\[D_n = \sup_x |F_n(x) - F(x)|\]

@@

The KS test is sensitive to both location and shape differences, but less powerful in detecting deviations in the tails of the distribution when compared to other tests like Shapiro-Wilk or Anderson-Darling.
\subsubsection*{2 sample KS test}
Follows the same principles, except it compares two ECDF's from two samples.
\subsection{Correlation Matrix}
A correlation matrix is a table that displays the pairwise correlation coefficients between multiple variables in a dataset. Each element in the matrix represents the degree of linear relationship between two variables, typically measured by Pearson's correlation coefficient:
\[r_{XY} = \frac{Cov(X,Y)}{\sigma_X\sigma_Y}\]

@@

\subsection{Gamma-Poisson distribution}

\subsection{Nelder - Mead optimization method}

\section{Discussion}
